TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2019-04-26 paper/draft.tex
rearrange citation

Advances in instrumentation with the lauch of several spectroscopic surveys in the past decade have dramatically increased the sample of known M dwarfs, and our potential to study M dwarf abundances on both exoplanet and galactic scales at a large statistical level.
The largest of such catalogs include the \citealt{West:2011} sample of 70,841 sources from the Sloan Digital Sky Survey (SDSS DR7; \citealt{Abazajian:2009}), and the \citealt{Yi:2014} and \citealt{Guo:2015} catalogs of 93,619 from the Large Sky Area Multi-Object Fiber Spectroscopic Telescope (LAMOST DR1; \citealt{Zhao:2012}), which each have determined spectral subtype classifications, H$\alpha$ equivalent width, and a number of optical molecular band index measurements. The launch of the (\apogee; \citealt{Majewski:2015}) survey as part of the Sloan Digital Sky Survey III mission \citep{Eisenstein:2011} has introduced the largest sample of M dwarfs observed with high resolution spectroscopy, yet pipeline measurements \citep{Perez:2016} of $\teff$ and $\feh$ have only been determined precise to 100\,K and 0.18\,dex down to $T_{\rm eff}\sim3550\,$K \citep{Schmidt:2016}.

>>>>

Advances in instrumentation with the lauch of several spectroscopic surveys in the past decade have dramatically increased the sample of known M dwarfs, and our potential to study M dwarf abundances on both exoplanet and galactic scales at a large statistical level (e.g. SDSS \citealt{West:2011}; LAMOST \citealt{Yi:2014} and \citealt{Guo:2015}).
The launch of the (\apogee; \citealt{Majewski:2015}) survey as part of the Sloan Digital Sky Survey III mission \citep{Eisenstein:2011} has introduced the largest sample of M dwarfs observed with high resolution spectroscopy, yet pipeline measurements \citep{Perez:2016} of $\teff$ and $\feh$ have only been determined precise to 100\,K and 0.18\,dex down to $T_{\rm eff}\sim3550\,$K \citep{Schmidt:2016}.
